### 2019-10-10 introduction.tex
some more intro done

%\IEEEraisesectionheading{\section{Introduction}}
\section{Introduction}
\label{sec:intro}
With a user base of more than one-tenth of the world's population,
spreadsheets are by far the most popular medium for ad-hoc exploration
and analysis of data by end-users~\cite{excel-users}. 
\saj{Studies show that information workers prefer to operate on their data within spreadsheets while shunning enterprise solutions 
with more advanced analytical features~\cite{chan1996use,raden2005shedding}. 
One popular joke among those developing business intelligence applications is that  the ``export to excel'' button is the third-most commonly used button from the menu bar, after OK and Cancel~\cite{bakke2016expressive}.}
Spreadsheets enable users to view, structure, and present data
in an intuitive tabular layout, wherein users can map their data and tasks;
this tabular layout is essential to
the popularity of spreadsheets~\cite{nardi1990spreadsheet}.

@@

So, how do we support more effective navigation of data
within spreadsheets?
One approach would be to try to integrate
an overview of the overall structure of the data along
with the spreadsheet~\cite{grudin2001partitioning}
\new{resulting in} a classical
overview+detail interface
where the spreadsheet is the detailed view.
Overview+detail interfaces are used
to facilitate navigation in various domains such as 
text editors and maps~\cite{cockburn2009review}.
\new{Users can manipulate
the overview or detailed view,
to perform high-level or low-level operations,
respectively.}
Overview+detail interfaces
have been shown to be effective in these domains,
reducing cognitive load for users by
providing \new{them} the big picture first,
helping them quickly assimilate 
the information space~\cite{cockburn2009review}.
\agp{got until here}
\saj{In this paper, our goal is to integrate an overview plug-in with spreadsheets that captures the overall structure of the data while allowing interactions that minimize the difficulties caused by typical navigational operations like scrolling and steering.}

@@

\squishlist
\item {\em Overview modality.}
\saj{One approach for an overview is to simply add a
zoomed out version of the entire sheet as a pane on the side,
as in popular presentation software applications like Microsoft PowerPoint or text editors
like Sublime Text. 
Unfortunately, this approach
would not suffice for a spreadsheet---while it would help users make
somewhat more informed
scrolling decisions, the zoomed out presentation of the overview would be unreadable. An overview should provide a comprehensible big picture view of the spreadsheet.
Another approach, adopted by map tools like the
early versions of Google maps,
is to use the overview
to provide a global context of the user's current location
being displayed in the zoomed in detailed view~\cite{cockburn2009review}.
While the overview remains static, users can perform semantic zooming operations~\cite{perlin1993pad} on the detailed
view which allows objects to be represented differently at different scales. Since spreadsheets already display the raw data,
zooming into and out of a detailed view consisting of
this raw data is not meaningful. Rather, the spreadsheet overview should dynamically change as users sought more fine-grained or coarse-grained view of the overall structure of the data.}

>>>>

%\IEEEraisesectionheading{\section{Introduction}}
\section{Introduction}
\label{sec:intro}
\new{With a user base of more than  one-tenth of the world's population,
{\bf \em spreadsheets are by far the most popular medium for ad-hoc exploration
and analysis of data}~\cite{excel-users}.} 
\saj{Studies show that information workers prefer to operate on their data within spreadsheets while shunning enterprise solutions 
with more advanced analytical features~\cite{chan1996use,raden2005shedding}. 
One popular joke among those developing business intelligence applications is that  the ``export to excel'' button is the third-most commonly used button from the menu bar, after OK and Cancel~\cite{bakke2016expressive}.}
Spreadsheets enable users to view, structure, and present data
in an intuitive tabular layout, wherein users can map their data and tasks;
this tabular layout is essential to
the popularity of spreadsheets~\cite{nardi1990spreadsheet}.

@@

So, how do we support more effective navigation of data
within spreadsheets?
One approach would be to try to integrate
an overview of the overall structure of the data along
with the spreadsheet~\cite{grudin2001partitioning}
\new{resulting in} a classical
overview+detail interface
where the spreadsheet is the detailed view.
Overview+detail interfaces are used
to facilitate navigation in various domains such as 
text editors and maps~\cite{cockburn2009review}.
\new{Users can manipulate
the overview or detailed view,
to perform high-level or low-level operations,
respectively.}
Overview+detail interfaces
have been shown to be effective in these domains,
reducing cognitive load for users by
providing \new{them} the big picture first,
helping them quickly assimilate 
the information space~\cite{cockburn2009review}.
\new{Our goal is to {\em integrate an overview plug-in 
with spreadsheets} that captures
the overall structure of the data,
while supporting interactions that address
the difficulties in typical navigational 
operations like scrolling and steering.
{\bf \em It is essential
that our interface is a plug-in that 
enhances the capabilities of spreadsheets
that so many users
are used to and reliant on,
as opposed to a potentially jarring or confusing 
replacement for spreadsheets.}
}
% \saj{In this paper, our goal is to integrate an overview plug-in with spreadsheets that captures the overall structure of the data while allowing interactions that minimize the difficulties caused by typical navigational operations like scrolling and steering.}

@@

\squishlist
\item {\em Overview modality.}
\saj{
One approach for an overview is to simply add a
zoomed out version of the entire sheet as a pane on the side,
as in popular presentation software like 
Microsoft PowerPoint or text editors
like Sublime Text. 
Unfortunately, this approach
would not suffice for a spreadsheet.
\new{An overview should provide a
comprehensible big picture view:
for a spreadsheet, when zooming out beyond a point, 
the overview would be effectively 
unreadable.}
Another approach, adopted by map tools like the
early versions of Google maps,
is to use the overview
to provide a global context of the user's current location
being displayed in the zoomed in detailed view~\cite{cockburn2009review}.
While the overview remains static, users can perform semantic zooming operations~\cite{perlin1993pad} on the detailed
view which allows objects to be represented differently at different scales. Since spreadsheets already display the raw data,
zooming into and out of a detailed view consisting of
this raw data is not meaningful. Rather, the spreadsheet overview should dynamically change as users seek a more fine-grained or coarse-grained view of the overall structure of the data.}
